The Astropy Project:

### 2017-09-23 main.tex
Adding infrastructure text: ci-helpers and package-template

\section{Infrastructure for affiliated packages}
\subsubsection{Package template}
% Brigitta may write this up if there is no other takers
\subsection{Continuous integration helpers}
% Brigitta
\subsection{sphinx extensions}
% Tom R

>>>>

\section{Infrastructure for affiliated packages}
% - should we use links to the appropriate github repo?
%
\par In addition to astronomy related packages and libraries, the Astropy
Project also contains and supports several infrastructure package that are
very generic. The following sections describes the most widely used
selection of them.
%
\subsubsection{Package template}
% Brigitta may write this up if there is no other takers
\par Astropy provides a template package that any Python package is welcome to
use (many affiliated packages do so). The template contains a ready-to-go
package layout. It provides infrastructure such as documentation tools,
testing framework and CI templates and configurations, Cython integration,
and documentation on how to make it all work.
%
\subsection{Continuous integration helpers}
% Brigitta
\texttt{ci-helpers} is a collection of scripts that empowers package
maintainers to control their testing set up and installation process for
various continuous integration services via a set of environment
variables. While the current development is mostly driven by the needs of
the astropy ecosystem, the actual usage of this package is extremely
widespread. Currently we support setups for TravisCI and AppveyorCI.
%
\subsection{sphinx extensions}
% Tom R
